---
title: "QCL-R-Workshop-L2"
author: "[YOUR NAME]"
date: "[TODAY's DATE]"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Hands-On 1
What is the difference in average uptake rates between chilled and nonchilled plants?
```{r, eval=F}
# your work here
```

### Hands-On 2
Create a new data.frame, `x`, with two variables, Plant and uptake, containing only non-chilled plant cases from CO2 dataset.
```{r, eval=F}
# your work here
```

### Hands-On 3
Now let's try chaining (piping) to create a new data.frame, `y`, with two variables, Plant and uptake, containing only non-chilled plant cases from CO2 dataset.
```{r, eval=F}
# your work here
```

### Hands-On 4
What are the three highest CO2 uptake cases? (Hint: descending order)
```{r eval=TRUE}
# your work here
```

### Homework Exercise 1 (Difficulty: low)
#### Import birth data and answer the questions below.

1. Import the data set, Births2015.csv, from https://raw.githubusercontent.com/jehopark/data_wrangling_with_r_beginners/master/Births2015.csv and save it as a new data frame named `births2015`.

2. What are the variable names?

3. What is the total number of babies born in 2015?

4. Create a data frame that contains the number of births on each day of the week in 2015. How many babies were born on Wednesday in 2015? (must use pipe operator)

5. Which date had the least amount of babies born?

### Homework Excercise 2 (Difficulty: medium-high) 
#### COVID-19 Cases in the U.S.
#### Try this when you have time later

Homework Exercise 2! (Solution skeleton)
========================================================
Create a barplot showing daily changes in the new COVID-19 cases in the US.

```{r, eval = FALSE}
library(readr) # need this for read_csv

fileurl <- " #_FILL-IN_# "
us_states <- read_csv(fileurl) 

names(us_states)

data_covid <- us_states %>% 
  #_FILL-IN_# # group_by
  #_FILL-IN_# # summarise
  #_FILL-IN_# # mutate and lag
barplot( #_FILL-IN_# ) # just a simple barplot with one argument 

# or use ggplot2 
require(ggplot2)
p <- data_covid %>% 
        ggplot(aes(x=date, y=daily_cases)) + 
        geom_bar(stat="identity", color="orange")
p
```
  
### Extra Hands-On: Add the seven day moving average line to the bar plot.
