---
title: "QCL-R-Workshop-L2"
author: "[YOUR NAME]"
date: "[TODAY's DATE]"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Hands-On 1
What is the difference in average uptake rates between chilled and nonchilled plants?
```{r, eval=F}
# your work here
```

### Hands-On 2
Create a new data.frame, `x`, with two variables, Plant and uptake, containing only non-chilled plant cases from CO2 dataset.
```{r, eval=F}
# your work here
```

### Hands-On 3
Now let's try chanining (piping) to create a new data.frame, `y`, with two variables, Plant and uptake, containing only non-chilled plant cases from CO2 dataset.
```{r, eval=F}
# your work here
```

### Hands-On 4
What are the three highest CO2 uptake cases? (Hint: descending order)
```{r eval=TRUE}
# your work here
```

### Homework Exercise 1 (Difficulty: low)
#### Import birth data and answer the questions below.
1. What are the variables?
2. What is the total number of babies born in 2015?
3. Make a histogram of number of births.  
4. How many babies were born on Wednesdays? (must use the pipe operator)
5. Which date had the least amount of babies born?

### Homework Excercise 2 (Difficulty: medium-high) 
#### COVID-19 Cases in the U.S.

Homework Exercise 2! (Solution skeleton)
========================================================
Create a barplot showing daily changes in the new COVID-19 cases in the US.

```{r, eval = FALSE}
library(readr) # need this for read_csv

fileurl <- " #_FILL-IN_# "
us_states <- read_csv(fileurl) 

data_covid <- us_states %>% 
  #_FILL-IN_# # group_by
  #_FILL-IN_# # summarise
  #_FILL-IN_# # mutate and lag
barplot( #_FILL-IN_# ) # just a simple barplot with one argument 

# or use ggplot2 
require(ggplot2)
p <- data_covid %>% 
        ggplot( #_FILL-IN_# ) + 
        geom_bar(stat="identity", color="orange")
p
```
  
### Extra Hands-On: Add the seven day moving average line to the bar plot.
